--- 
title: "Applications of Machine Learning in Imputation"
author: "Methodology"
date: "2019"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    split_by: section
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: Vinayak-NZ/ML-Imputation
description: "This document presents the findings from the 2018/19 project into the use of machine learning in imputation."
---

# Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r package-doc, message=FALSE, echo=FALSE}
source("R/WF1_package_load.R")
```

```{r external, include=FALSE}
knitr::read_chunk("R/WF1_package_load.R")
knitr::read_chunk("R/WF2_data_prep.R")
knitr::read_chunk("R/WF3_data_study.R")
knitr::read_chunk("R/WFM_EconAct.R")
knitr::read_chunk("R/WFM_HoursCont.R")
knitr::read_chunk("R/WFM_SocialGrade.R")
knitr::read_chunk("R/WFM_Student.R")
```

Editing and imputation are both methods of data processing. Editing refers to the detection and correction of errors in the data, whilst imputation is a method of correcting errors in a dataset [@deWaal]. This document presents findings from work carried out at the Office for National Statistics on the use of machine learning in imputation. The chapters address the following questions:  
  
1) What is imputation?  
2) What is machine learning?  
3) Why use machine learning?  
4) How XGBoost works?  
5) Methods used for the investigation  
6) Results of the investigation  
7) Conclusions and future direction  